\section{Limitations and Future Work}

\subsection{Design Scope Limitations}

The wing box design presented in this report is intended as a conceptual structural study. As such, several aspects of detailed aircraft structural design were intentionally excluded to maintain focus on structural layout and load-path reasoning.

No finite element stress analysis was performed, and skin thicknesses and spar dimensions were not optimized through numerical sizing. Buckling behavior, fatigue life, and damage tolerance were also not evaluated. Additionally, internal ribs, fasteners, and attachment fittings were not explicitly modeled in the CAD geometry.

These limitations are consistent with early-stage design practice, where architectural decisions are established prior to detailed structural sizing and certification analysis.

%------------------------------------------------

\subsection{Opportunities for Further Development}

The wing box architecture developed in this study provides a strong foundation for future refinement. Potential extensions of this work include:

\begin{itemize}
    \item Finite element analysis to evaluate stress distribution and identify critical load paths
    \item Buckling analysis of compression skins under positive maneuvering loads
    \item Material trade studies comparing aluminum and composite constructions
    \item Integration of internal ribs and wing root attachment features
    \item Weight optimization and structural efficiency assessment
\end{itemize}

These developments would enable progression from conceptual design toward a preliminary or detailed structural design phase.

%------------------------------------------------

\subsection{Portfolio and Professional Context}

This project is intended to serve as a portfolio-quality demonstration of structural reasoning, CAD execution, and engineering communication. The modular structure of the design and documentation allows for incremental upgrades as additional analysis capabilities are developed.

As such, the project reflects a realistic engineering workflow rather than a finalized or certification-ready design.